## Data Set 2 (ds2) Despcription:
    
    The data are MC generated (see below) to simulate registration of high energy gamma particles and hadron particles in a        ground-based atmospheric Cherenkov gamma telescope using an imaging technique.
    
    I'm trying to predict whether the particles are gamma or hadron based on predictors 1-10 described in the attribute            description.
    
    I have performed logistic regression and kNN classification on the data.
    
    Number of Instances: 19020
    Number of Attributes: 11 (including target)
    
    Attribute Description:
    
        1.   fLength:  continuous  # major axis of ellipse [mm]
        2.   fWidth:   continuous  # minor axis of ellipse [mm] 
        3.   fSize:    continuous  # 10-log of sum of content of all pixels [in #phot]
        4.   fConc:    continuous  # ratio of sum of two highest pixels over fSize  [ratio]
        5.   fConc1:   continuous  # ratio of highest pixel over fSize  [ratio]
        6.   fAsym:    continuous  # distance from highest pixel to center, projected onto major axis [mm]
        7.   fM3Long:  continuous  # 3rd root of third moment along major axis  [mm] 
        8.   fM3Trans: continuous  # 3rd root of third moment along minor axis  [mm]
        9.   fAlpha:   continuous  # angle of major axis with vector to origin [deg]
        10.  fDist:    continuous  # distance from origin to center of ellipse [mm]
        11.  class:    g,h         # gamma (signal), hadron (background)
    
    Target Distribution:
        g = gamma (signal):     12332
        h = hadron (background): 6688
    
    The data set is obtained from "http://archive.ics.uci.edu/ml/machine-learning-databases/magic/"
    The data is in magic04.data "http://archive.ics.uci.edu/ml/machine-learning-databases/magic/magic04.data"
    For full citation see the citation section at the end.


```{r}
ds2 <- read.table("C:/Users/ADMIN/Desktop/Academia 2.0/Junior/Spring 2018/Machine Learning/HW/magic04.data", header=FALSE, sep=",")
```


Adding column names for easy interpretation.
```{r}
colnames(ds2) <- c("fLength","fWidth","fSize","fConc","fConc1","fAsym","fM3Long","fM3Trans","fAlpha","fDist","class")
```

Using R functions to gauge data set.

```{r}
dim(ds2)
summary(ds2)
```


```{r}
names(ds2)
head(ds2)
str(ds2)
```

```{r}
par(mfrow=c(1,2))
cdplot(ds2$class~ds2$fSize)
cdplot(ds2$class~ds2$fAlpha)
```
From the first cdplot we can see that gamma particles tend to have smaller size.
From the second cdplot we can see that gamma particles tend to have lower alpha.


Splitting the data randomly into 75% train and 25% test.

```{r}
set.seed(1234)
i <- sample(nrow(ds2), nrow(ds2)*0.75, replace=FALSE)
train <- ds2[i,]
test <- ds2[-i,]
```

Creating logistic model with class as the target and fLength, fWidth, fSize, fConc, fConc1, fAsym, fM3Long, fM3Trans, fAlpha and fDist, as predictors

```{r}
glm1 = glm(class~., data=train, family=binomial)
probs <- predict(glm1, newdata=test, type="response")
pred <- ifelse(probs>0.5, "h", "g")
table(pred, test$class)
```


```{r}
summary(glm1)
```

Calculating te accuracy of the model.

```{r}
paste("accuracy = ", sum(pred==test$class)/NROW(test$class)*100, "%")
```


Splitting the data randomly into 75% train and 25% test.

```{r}
set.seed(1234)  # setting a seed gets the same results every time
ind <- sample(2, nrow(ds2), replace=TRUE, prob=c(0.75, 0.25))
ds2.train <- ds2[ind==1, 1:10]
ds2.test <- ds2[ind==2, 1:10]
ds2.trainLabels <- ds2[ind==1, 11]
ds2.testLabels <- ds2[ind==2, 11]
```

Performing kNN classification on the data. The predictors are the same as the ones for the logistic model.

```{r}
library(class)
ds2_pred <- knn(train=ds2.train, test=ds2.test, cl=ds2.trainLabels, k=10)
```


```{r}
summary(ds2_pred)
```
Summary doesn't tell us much.

Calculating accuracy.

```{r}
results <- ds2_pred == ds2.testLabels
acc <- length(which(results==TRUE)) / length(results)
acc
```


## Analysing Models/Algorithm Results:

    Both logistic model and kNN classification have good accuracy.
    
    The logistic model has an accuracy of 79.9158780231335%.
    
    kNN classification gives us an accuracy of 80.62949%.
    
    kNN classifiaction gives is slightly better for this data set.

## Citations:
    1. Data Set 2 (Gamma and hadron particle data set)
    
        [1] Lichman, M. (2013). UCI Machine Learning Repository                                                                            [http://archive.ics.uci.edu/ml/machine-learning-databases/magic/]. Irvine, CA: University of California, School of             Information and Computer Science.
